Capturing underlying musical structure: an audio-based approach using deep learning

### 2023-02-10 introduction/introduction.tex
Updates from Overleaf

Music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition. It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} Structure Analysis (MSA) is the field of study that aims to understand music's underlying organization and structure.

MSA is a multidisciplinary field that draws on techniques from music theory, signal processing, machine learning, and other areas. It can be applied to various musical styles and genres and has been used for tasks such as music transcription, generation, and similarity.

@@

As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and the underlying relationship among them. I am deeply interested in learning how to retrieve embedded information within music. The study of music structure analysis provides a means to systematically analyze and understand musical pieces. It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.

@@

As a professional music transcriber, I am interested in understanding how deep neural networks (DNNs) filter musical features. In other words, I am eager to learn how DNNs listen~\cite{7500246} to music.

By studying music structure analysis using musically motivated neural networks, you will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music. Additionally, we will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}

>>>>

This master thesis investigates the interrelationship between music\footnote{The term "music" used in this context refers specifically to Western tonal music tradition. It is assumed that the musical structures and elements discussed are based on this tradition and may not apply to other musical styles or cultures.} structure analysis, aural skills, and the underlying musical structure in musical composition. Musical elements, including melody, harmony, rhythm, and form, constitute music structure analysis.

Aural skills encompass perceptual and cognitive abilities, enabling individuals to comprehend musical works through listening. These skills encompass the ability to differentiate musical elements, comprehend relationships between them, and discern the structure of a musical composition.

The underlying musical structure refers to the systematic arrangement of musical elements that results in a coherent and expressive musical work.

This master thesis investigates the interplay between music structure analysis, aural skills, and the underlying musical structure through a comprehensive analysis of musical works from diverse styles and genres. By utilizing computational techniques from Music Information Retrieval (MIR) and incorporating a musicological perspective to contextualize the findings, this thesis aspires to offer a fresh and insightful examination of these components of musical composition and further our understanding of their relationships.

@@

As a music lover and connoisseur, I am interested in gaining a deeper understanding of the fundamental building of musical composition, the various techniques used to create musical works, and capturing underlying relationships among them. I am deeply interested in learning how to retrieve embedded information within music. The study of music structure analysis provides a means to systematically analyze and understand musical pieces. It has traditionally been approached through music theory, formal musical notation, musical analysis techniques, and machine learning, which I plan to blend.

@@

As a professional musician and music transcriber, I am interested in understanding how deep neural networks (DNNs) filter musical features. In other words, I am eager to learn how DNNs listen~\cite{7500246} to music.

By studying music structure analysis using musically motivated neural networks, we will gain an in-depth understanding of the latest advancements in the field and how these techniques are being used to revolutionize our understanding of music. Additionally, we will be able to contribute to developing new and innovative methods for musical analysis~\cite{Huang2019MusicTG}

### 2023-02-10 music analysis/MSA.tex
Updates from Overleaf

Given a self-similarity matrix S, the novelty curve can be computed by taking the row-wise sum of the self-similarity matrix and normalizing the values. The novelty curve measures the deviation from the average similarity across time frames and can be used for various audio analysis tasks such as beat tracking or segmentation.

@@

Schenkerian analysis uses specialized musical notation and is either presented in a generative manner, starting from the Ursatz and ending at the score or in a reductive manner, starting from the score and reducing it to its fundamental structure. The Ursatz is presented in an arrhythmic graph, and rhythmic signs display hierarchical relationships between events.\footnote{In Schenkerian analysis, structural levels refer to the representation of a piece of music at different levels of abstraction. These levels typically include the foreground, middle ground, and background. Schenker posits that musical form, as represented through these structural levels, can be understood as an energy transformation, specifically the transformation of forces that flow from the background to the foreground through the various levels.}

@@

Aural music skills are the capacity to comprehend and analyze musical compositions through listening. These skills encompass a wide range of abilities, including identifying musical elements such as rhythm, melody, harmony, timbre, and form, performing music from memory, and transcribing audio recordings into written musical scores.

@@

Aural music skills are crucial not only for an individual's personal musical growth but also for gaining a deeper understanding of the underlying musical structure of a piece. Identifying and analyzing musical elements through listening allows one to comprehend the relationships between these elements and how they contribute to the overall musical structure. This ability to perceive and understand musical structure is fundamental to making informed decisions and interpretations.

@@

Moreover, aural skills also play an essential role in preserving and continuing musical traditions, as they allow musicians to accurately pass down and preserve the musical heritage of their culture. By recognizing and understanding the underlying musical structures of traditional music, musicians can maintain the authenticity of the music and ensure its continuation for future generations.

In conclusion, aural music skills are crucial for personal musical growth and for gaining a deeper understanding of the musical structure, effective musical communication and collaboration, and the preservation of musical traditions.

>>>>

Given a self-similarity matrix S, the novelty curve can be computed by taking the row-wise sum of the self-similarity matrix and normalizing the values. The novelty curve measures the deviation from the average similarity across time frames.

@@

Schenkerian analysis uses specialized musical notation and is either presented in a generative manner, starting from the Ursatz and ending at the score or in a reductive manner, starting from the score and reducing it to its fundamental structure. The Ursatz is presented in an arrhythmic graph, and rhythmic signs display hierarchical relationships between events. \footnote{In Schenkerian analysis, structural levels refer to the representation of a piece of music at different levels of abstraction. These levels typically include the foreground, middle ground, and background. Schenker posits that musical form, as represented through these structural levels, can be understood as an energy transformation, specifically the transformation of forces that flow from the background to the foreground through the various levels.}

@@

Aural music skills are the capacity to comprehend and analyze musical compositions through listening. These skills include identifying musical elements such as rhythm, melody, harmony, timbre, and form, performing music from memory, and transcribing audio recordings into written musical scores.

@@

Aural music skills are crucial not only for an individual's personal musical growth but also for gaining a deeper understanding of the underlying musical structure of a piece. Identifying and analyzing musical elements through listening allows one to comprehend their relationships and how they contribute to the overall musical structure. This ability to perceive and understand musical structure is fundamental to making informed decisions and interpretations.

@@

Moreover, aural skills also play an essential role in preserving and continuing musical traditions, as they allow musicians to accurately pass down and preserve the musical heritage of their culture. By recognizing and understanding the underlying musical structures of traditional music, musicians can maintain its authenticity and ensure its continuation for future generations.

In conclusion, aural music skills are crucial for personal musical growth and a deeper understanding of the musical structure, effective musical communication, collaboration, and preserving musical traditions.
